The World Bank, Women, Business and the Law

### 2024-02-19 outputs/paper/paper.qmd
finish graphs, edit some of the paper

---
title: "Women and Gender Pay Gap "
subtitle: "Faulty World Bank Data Conflicts: A Canadian Example"
author: 
  - Sehar Bajwa
  - Luca Carnegie
thanks: "Code and data are available at: https://github.com/lcarnegie/replicationpaper. "
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

```{r}
#| include: false
#| warning: false
#| message: false

library(tidyverse)
```

@@

@@

>>>>

---
title: "The World Bank, Women, Business and the Law"
subtitle: "The Need for better checking of Data"
author: 
  - Sehar Bajwa
  - Luca Carnegie
thanks: "Code and data are available at: https://github.com/lcarnegie/replicationpaper. "
date: February 20, 2024
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

```{r workspace-setup}
#| include: false
#| warning: false
#| message: false

library(tidyverse)

## WBL Dataset Setup

wb_data <- read_csv(here::here("outputs/data/wb_data_clean.csv"))
```

@@

## Source {#subsec1-data}
## Methodology {#subsec2-data}

@@

::: {#refs}
:::
